Graphs for 1000  Generations

### 2021-07-10 graphs_newt_snakes/fig_1000.Rmd
I am turning the r figures and data collection into functions its more difficult than I thought. I also worked on creating a bash script that can do two different loops to go through files in a folder and to use a csv to pull different varaables. This script worked very well!.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
library(colorspace)
#setwd("~/Desktop/Proposal Old Drafts")
```

@@

```{r data from the mistake folder, echo=FALSE}
newt_max_pheno_1 = 0
snake_max_pheno_1 = 0
newt_min_pheno_1 = 0
snake_min_pheno_1 = 0
true_max_1 = 0
true_min_1 = 0
min_difference_1 = 0
max_difference_1 = 0

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

@@

@@

  print(paste0("Newt max pheno: ", newt_max_pheno_1))
  print(paste0("Snake max phenot: ", snake_max_pheno_1))
  print(paste0("Newt min pheno: ", newt_min_pheno_1))
  print(paste0("Snake min Pheno: ", snake_min_pheno_1))

@@

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Wrong1sim: Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes (Log)")+
  theme_bw()

@@

This figure represents the difference between the snake and the newt phenotype. The pick lines indicat that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
library(colorspace)

#setwd("~/Desktop/Proposal Old Drafts")
```

@@

```{r functions, echo=FALSE}

collect_data_points <- function(files) {
  newt_max_pheno_1 = 0
  snake_max_pheno_1 = 0
  newt_min_pheno_1 = 0
  snake_min_pheno_1 = 0
  true_max_1 = 0
  true_min_1 = 0
  min_difference_1 = 0
  max_difference_1 = 0
  mean = 0
  sd = 0

@@

  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  mean = mean(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno))
  sd = sd(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno))

@@

@@

  return(c(newt_max_pheno_1, snake_max_pheno_1, newt_min_pheno_1, snake_min_pheno_1, true_max_1, true_min_1, min_difference_1, max_difference_1, mean, sd))
}

phenotype_graph <- function(files, the_mean, the_sd, title){

  file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  scale_y_log10(limits=c(the_mean-(the_sd*10), the_mean+(the_sd*10)))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle(title) +
  xlab("Generation") + ylab("Average Phenotypes (Log)")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)
}
return(p)
}

differnce_graph <- function(files, the_mean, the_sd, title){

  p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  #scale_y_log10(limits=c(min_difference_1, max_difference_1))+
  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
    ggtitle(title) +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

}
  return(p)
}

```{r data from the mistake folder, echo=FALSE}
files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files)

newt_max_pheno_1 = out[1]
snake_max_pheno_1 = out[2]
newt_min_pheno_1  = out[3]
snake_min_pheno_1 = out[4]
true_max_1 = out[5]
true_min_1 = out[6]
min_difference_1 = out[7]
max_difference_1 = out[8]
my_mean = out[9]
my_sd = out[10]

print(paste0("Newt max pheno: ", newt_max_pheno_1))
print(paste0("Snake max phenot: ", snake_max_pheno_1))
print(paste0("Newt min pheno: ", newt_min_pheno_1))
print(paste0("Snake min Pheno: ", snake_min_pheno_1))
print(paste0("Mean of combined snake and newt: ", my_mean))
print(paste0("Sd of combined snake and newt: ", my_sd))

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
title="Wrong1sim: Phenotype Measurements for Newts and Snakes"
p = phenotype_graph(files, my_mean, my_sd, title)

@@

This figure represents the difference between the snake and the newt phenotype. The pink lines indicate that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts
